### 2023-11-11 manuscript/manuscript.Rmd
correct sentence about mass accuracy for metabolite annotation
Clarify what transformations can be used

Ultra-high resolution MS instrumentation utilising Orbitrap mass analyser technology is now commonplace in many laboratories, which can yield many thousands of *m/z* features in a single analytical run [@hu2005].
This has provided an unprecedented opportunity for metabolite annotation and has been applied to direct infusion approaches like flow infusion electrospray high-resolution MS (FIE-HRMS), commonly applied for 'first pass' metabolome fingerprinting and liquid chromatography (LC) HRMS profiling for non-targeted metabolomic analyses.
However, mass accuracy alone does not meet the requirements for metabolite annotation [@kind2006].

@@

This approach was designed for use with any sample tissues and fluids of biological origin and analysed using non-targeted ultra-high resolution mass accuracy ESI-MS data.
The additional input of knowledge for transformations specific to the biological sample can increase assignment success.
However, the approach could be applied without the use of transformations where these are not relevant.
The assigned molecular formulas could be putatively matched to compound databases such as KEGG using ionisation rules such as those of the MZedDB database and then apply functional enrichment analyses using a tool such as the R package *FELLA* [@draper2009;@picart2018].
They could also be used to provide some information about precursor ions in LC-MS/MS fragmentation analyses.

>>>>

Ultra-high resolution MS instrumentation utilising Orbitrap mass analyser technology is now commonplace in many laboratories, which can yield many thousands of *m/z* features in a single analytical run [@hu2005].
This has provided an unprecedented opportunity for metabolite annotation and has been applied to direct infusion approaches like flow infusion electrospray high-resolution MS (FIE-HRMS), commonly applied for 'first pass' metabolome fingerprinting and liquid chromatography (LC) HRMS profiling for non-targeted metabolomic analyses.
However, high mass accuracy alone is insufficient for unambiguous metabolite annotation [@kind2006].

@@

This approach was designed for use with any sample tissues and fluids of biological origin and analysed using non-targeted ultra-high resolution mass accuracy ESI-MS data.
The additional input of knowledge for transformations specific to the biological sample can increase assignment success.
These transformations could encompass any biological or non-biological alteration that may occur to the precursor molecules and result in correlated *m/z* that could be used for molecular formula assignment.
In-source fragmentation would be one such example.
The approach can alternatively be applied without the use of transformations where these are not relevant.
The assigned molecular formulas could be putatively matched to compound databases such as KEGG using ionisation rules such as those of the MZedDB database and then apply functional enrichment analyses using a tool such as the R package *FELLA* [@draper2009;@picart2018].
They could also be used to provide some information about precursor ions in LC-MS/MS fragmentation analyses.
